---
title: "Student Sit In"
author: "Sandra Rogers"
date: "10/28/2019"
output: 
  html_document:
    toc: true
    number_sectons: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ONE SHOT assignment!
this is an extra credit assignment, must be completed Monday Oct 28, turn-in closes at midnight!

## Problem statement: 
Students at UCD- is there a relation between where one sits and one's major? 

## Introduction  

<!-- where is the data found?  Is this an experiment or an observational study?  !-->

Data from this study came from UC Davis and is an observational study.



```{r include=FALSE, echo=FALSE}
library(tigerstats)
data(ucdavis1)

```

$H_0$: there is no relationship between one's major and where one sits in a class   
$H_A$: where one sits in class and one's major are related  

<!-- Get the data: !-->

names of the data in the data frame

```{r echo=FALSE}
UCDdataframe = data.frame(seat=ucdavis1$Seat, major=ucdavis1$class, data=ucdavis1)
names(UCDdataframe)
```
## Methods

<!--  describe analysis methods here 
what are the variable types, and indicate gaphical, numerical, and inferential methods appropriate
for this question  !--> 

Both variables are categorical, so we use bargraphs and tables for the data and a chi-squared test for inference. 

## Data summary

**Graphical summary**
put the graphic description of the data here

```{r}
barchartGC(~seat+major, data=UCDdataframe, main='Seating & Major' , type='percent', xlab='Seating')
```

This bargraph shows that most students with a liberal arts major tend to sit more towards the front of a class rather than the back, with a higher percentage of non-liberal arts students sitting towards the back.



**Numerical summary**
put numerical summary here

```{r}
tab1 = xtabs(~seat+major, data=UCDdataframe)
rowPerc(tab1)
```

This data shows that most students with a liberal arts major tend to sit more towards the front of a class rather than the back, with a higher percentage of non-liberal arts students sitting towards the back.


## Inferential Results
put the inferential test for the the null hypothesis here

```{r}
chisqtestGC(tab1)
```

The P-value for the chi-square test is 0.2173


## Results and conclusions

<!-- explain-- is there evidence that certain majors tend to sit in particular areas of the class?  Can the results of this test be generalized to all majors in all universities? !-->


The P-value for the chi-square test is 0.2173 > 0.05 so we failed to reject the null hypothesis and conclude we have no evidence to support the contention that people's major is related to where they choose to sit.


<!--
push results to your github account, turn in the URL

--OR--

If you did not fork my repo to your github account,
create a repository in your github account for this project, get the URL for that repo and 
(in the terminal window..)

$git remote add origin URL_of_your_github_repo
$git push -u origin master

!-->